\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS-------------------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://jasonjunjiezhu.com}{\Large Jason Junjie Zhu}} & Email: \href{mailto:junjie.zhu.jason@gmail.com}{junjie.zhu.jason@gmail.com}\\
  \href{http://jasonjunjiezhu.com}{jasonjunjiezhu.com} & Mobile: \href{tel:+16502857123}{650-285-7123} \\
\end{tabular*}

%-----------SUMMARY-----------------
\section{Summary}
I am a curiosity-driven builder with experience in Statistics and AI methodology (TODO: fill in later)
and real-world systems (multi-modal RAGs, search products, biomedical discovery), drawn to hidden patterns, scalable impact, and high-agency teams.

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Stanford University}{Stanford, CA}
      {Ph.D. in Electrical Engineering (Advisor: Chiara Sabatti), M.S. in Statistics}{2014 -- 2020}
    \resumeSubheading
      {Franklin W. Olin College of Engineering}{Needham, MA}
      {B.S. in Electrical and Computer Engineering}{2010 -- 2014}
  \resumeSubHeadingListEnd

%-----------PROFESSIONAL EXPERIENCE-----------------
\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Nexa AI}{Cupertino, CA}
      {Head of AI/ML}{Feb 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Leadership}
          {Leading a lean and fast-paced team to accelerate Gen-AI edge inference on any device.}
        \resumeItem{Local RAGs}
          {Developing privacy-preserving RAGs with small AI models and on-device vision capabilities.}
        \resumeItem{Agentic Systems}
          {Researching action-driven applications with new AI protocols (e.g., MCP, A2A).}
      \resumeItemListEnd

    \resumeSubheading
      {Apple}{Cupertino, CA}
      {Machine Learning Engineer}{Jan 2020 -- Feb 2025}
      \resumeItemListStart
        \resumeItem{Evaluation}
          {Developed both generative and retrieval-based methods to evaluate query understading and ranking systems.}
        \resumeItem{Data Analysis}
          {Analyzed complex production data sets with high-dimensional statistics and large-scale computing.}
        \resumeItem{Testing Strategies}
          {Designed new testing strategies for software services at the intersection of user experience and computational algorithms.}
      \resumeItemListEnd

    \resumeSubheading
      {Illumina}{San Francisco Bay Area}
      {Deep Learning Scientist (Internship)}{Jun 2017 -- Aug 2017}
      \resumeItemListStart
        \resumeItem{TensorFlow}
          {Wrote customized deep learning software in TensorFlow and experimentation infrastructure for base-calling applications.}
        \resumeItem{Model Architectures}
          {Systematically combined CNNs, RNNs, and residual networks to significantly improve accuracy.}
      \resumeItemListEnd

    \resumeSubheading
      {10X Genomics}{Pleasanton, CA}
      {Data Scientist (Internship)}{Jun 2016 -- Aug 2016}
      \resumeItemListStart
        \resumeItem{R/Python Pipelines}
          {Productionized R software packages for exploratory single-cell RNA sequencing analysis and improved internal Python software pipelines.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------RESEARCH EXPERIENCE-----------------
\section{Research Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Department of Statistics, Stanford University}{Stanford, CA}
      {Researcher}{Sep 2016 -- Feb 2020}
      \resumeItemListStart
        \resumeItem{Gene Ontology}
          {Developed graph visualizations to interpret and analyze the Gene Ontology.}
        \resumeItem{Single-cell RNA-seq}
          {Implemented exploratory data analysis pipelines for stem-cell and cancer model systems.}
        \resumeItem{Selective Inference}
          {Proposed selective inference methods to study tissue-specific expression quantitative trait loci.}
      \resumeItemListEnd

    \resumeSubheading
      {Department of Computer Science, Stanford University}{Stanford, CA}
      {Researcher}{Sep 2014 -- Sep 2016}
      \resumeItemListStart
        \resumeItem{Sequence Alignment}
          {Designed algorithms in C/C++ to improve speed and accuracy of state-of-the-art sequence aligners for linked-read data.}
      \resumeItemListEnd

    \resumeSubheading
      {Wireless Communication Group, Olin College}{Needham, MA}
      {Researcher}{Sep 2010 -- May 2014}
      \resumeItemListStart
        \resumeItem{SDMA Networks}
          {Proposed stochastic geometric interference models to extend SDMA network applications.}
      \resumeItemListEnd

    \resumeSubheading
      {Graph Theory Research Group, Olin College}{Needham, MA}
      {Researcher}{Dec 2011 -- May 2014}
      \resumeItemListStart
        \resumeItem{Graph Coloring}
          {Investigated frequency assignment in wireless networks through graph coloring.}
        \resumeItem{L(2,1)-labeling}
          {Found minimum span for L(2,1)-labeling in various graph families.}
      \resumeItemListEnd

    \resumeSubheading
      {Signal Processing and Communication Laboratory, HKUST}{Hong Kong}
      {Researcher}{Jul 2013 -- Sep 2013}
      \resumeItemListStart
        \resumeItem{OFDM Systems}
          {Studied unsynchronized interferers in multi-antenna OFDM systems.}
        \resumeItem{Linear Receivers}
          {Discovered closed-form solutions for typical linear receiver performance.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------SELECTED PUBLICATIONS-----------------
\section{Selected Publications}
  \resumeSubHeadingListStart
    \resumeSubItem{Improving ML-based information retrieval software with user-driven functional testing and defect class analysis}
      {FST, 2022}
    \resumeSubItem{Automatically Authoring Regression Tests for Machine-Learning-Based Systems}
      {ICSE, 2021}
    \resumeSubItem{Progenitor identification and SARS-CoV-2 infection in human distal lung organoids}
      {Nature, 2020}
    \resumeSubItem{Exploratory gene ontology analysis with interactive visualization}
      {Scientific Reports, 2019}
    \resumeSubItem{Visualization and analysis of single-cell RNA-seq data by kernel-based similarity learning}
      {Nature Methods, 2017}
  \resumeSubHeadingListEnd

%-----------GOOGLE SCHOLAR-----------------

%-------------------------------------------
\end{document}
